\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-12-02 paper.qmd
Need to work on projections again

@@

@@

pbmc_proj_umap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2)) +
  geom_segment(
    data = model_df,
    aes(
      x = proj1_from,
      y = proj2_from,
      xend = proj1_to,
      yend = proj2_to),
    color = "#000000") +
  geom_point(
    #size = 0.5,
    alpha = 0.2,
    color = '#a65628') +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2),
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 0.75)) +
  ylim(c(-1, 0.75)) +
  interior_annotation("a3", cex = 2)
```

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the layout a, and two views of the fit in projections from $50\\text{-}D$, for the PBMC3k data ($n =  5858$ and $p = 50$). Layout shows close clusters. In $50\\text{-}D$, the data shows "
#| label: fig-model-pbmc-author-proj-scdeed
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-height: 80%

free(trimesh_removed_pbmc) + 
  pbmc_proj_umap_model1 + 
  pbmc_proj_umap_model2 + 
  plot_layout(nrow=3) &
  theme(legend.position='none')
```

>>>>

projection_scaled <- projection * 3

@@

axes_obj <- gen_axes(
  proj = projection,
  limits = 0.04,
  axis_pos_x = -0.025,
  axis_pos_y = -0.025,
  axis_labels = names(scaled_pbmc_data),
  threshold = 0.0001)

pbmc_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_point(
    #size = 0.5,
    alpha = 0.2,
    color = '#a65628') +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.03, 0.06)) +
  ylim(c(-0.03, 0.06)) +
  interior_annotation("a2", cex = 2)

@@

axes_obj <- gen_axes(
  proj = projection,
  limits = 0.03,
  axis_pos_x = -0.02,
  axis_pos_y = -0.02,
  axis_labels = names(scaled_pbmc_data),
  threshold = 0)

pbmc_proj_umap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2)) +
  geom_segment(
    data = model_df,
    aes(
      x = proj1_from,
      y = proj2_from,
      xend = proj1_to,
      yend = proj2_to),
    color = "#000000") +
  geom_point(
    #size = 0.5,
    alpha = 0.2,
    color = '#a65628') +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2),
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.025, 0.02)) +
  ylim(c(-0.025, 0.02)) +
  interior_annotation("a3", cex = 2)
```

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the layout a, and two views of the fit in projections from $50\\text{-}D$, for the PBMC data ($n =  5858$ and $p = 50$). Layout shows close clusters. In $50\\text{-}D$, the data shows "
#| label: fig-model-pbmc-author-proj-scdeed
#| fig-pos: H
#| fig-width: 15
#| fig-height: 5
#| out-height: 80%

free(trimesh_removed_pbmc) + 
  pbmc_proj_umap_model1 + 
  pbmc_proj_umap_model2 + 
  plot_layout(ncol=3) &
  theme(legend.position='none')
```

### 2024-12-02 paper.tex
Need to work on projections again

\caption{\label{fig-model-pbmc-author-proj-scdeed}Model in \gD{}, on the
layout a, and two views of the fit in projections from \(50\text{-}D\),
for the PBMC3k data (\(n =  5858\) and \(p = 50\)). Layout shows close
clusters. In \(50\text{-}D\), the data shows}

>>>>

\caption{\label{fig-model-pbmc-author-proj-scdeed}Model in \gD{}, on the
layout a, and two views of the fit in projections from \(50\text{-}D\),
for the PBMC data (\(n =  5858\) and \(p = 50\)). Layout shows close
clusters. In \(50\text{-}D\), the data shows}
